\documentclass[11pt]{tracv}
\usepackage[margin=2cm]{geometry}
\frenchspacing

\name{Arman Bilge}
\address{Room 376, Building 303S \\ Department of Computer Science}{The University of Auckland}{Private Bag 92019}{Auckland 1142, New Zealand}
\phone{+64 9 373 7599 ext. 87458}
\email{arman@armanbilge.com}
\website{www.armanbilge.com}

\begin{document}

    \null

    \head

    \begin{columnsection}{Education}
        \columnentry{B.Sc. in Computer Science and Mathematics}{The University of Auckland}{March 2014--November 2016 (expected)}{Auckland, New Zealand}{}{}{}
    \end{columnsection}

    \begin{columnsection}{Research Experience}

        \columnentry{Undergraduate Researcher}{The University of Auckland}{Computational Evolution Group}{Auckland, New Zealand}{Department of Computer Science}{March 2014--Present}{}

        \columnentry{High School Intern}{Massachusetts Institute of Technology}{Computational Biology Group}{Cambridge, Massachusetts}{Computer Science and Artificial Intelligence Laboratory}{March 2013--February 2014}{}

        \columnentry{High School Intern}{Harvard University}{Girguis Laboratory}{Cambridge, Massachusetts}{Department of Organismic and Evolutionary Biology}{January 2013--February 2014}{}

    \end{columnsection}

    \begin{columnsection}{Teaching Experience}

        \columnentry{Instructor}{Lexington High School}{Phylogenetics/Computational Biology Club}{Lexington, Massachusetts}{Science and Mathematics Departments}{October 2012--February 2014}{}

    \end{columnsection}

    \begin{hangingsection}{Presentations}

        \hangingentry \textbf{A. Bilge} (July 2012). Investigating evolution via computational biology: The application of phylogenetic analyses to epidemiology and ecology. \emph{XSEDE12}, Chicago, IL. Invited; received NSF funding for travel and accomodation.

    \end{hangingsection}

    \begin{hangingsection}{Honors and Awards}

        \hangingentry \textbf{\$5,000 Summer Scholarship}, The Allan Wilson Centre for Molecular Ecology and Evolution (October 2014).

        \hangingentry \textbf{\$50,000 Scholarship Individual Winner}, Siemens Competition in Math, Science and Technology (December 2013).

        \hangingentry \textbf{1st and 2nd Places}, Massachusetts State Science and Engineering Fair (May 2012 and 2013).

    \end{hangingsection}

\end{document}
